Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-11 paper/paper.tex
Fix SPSS DD algorithm
added SPDS algorithm and example

\section{Algorithms}
\subsection{Dynamic Provisioning Dynamic Scheduling (DPDS)}

@@

@@

\begin{algorithm}
\caption{Ensemble planning algorithm}
\label{alg:admit}
\begin{algorithmic}[1]
\Require W: workflow ensemble, b: budget, d: deadline
\Ensure Schedule as much of W as possible given b and d
\Procedure{PlanEnsemble}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{DAG planning algorithm}
\label{alg:plandag}
\begin{algorithmic}[1]
\Require $w$: DAG, $P$: current plan, $d$: deadline
\Ensure Create plan for $w$ that minimizes cost and meets deadline $d$
\Procedure{PlanDAG}{$w,P,d$}
    \State $P^\prime\gets$ copy of $P$
    \State \Call{DeadlineDistribution}{w,d}
    \For{$t\ in\ w\ sorted\ by\ Deadline(t)$}
        \State Choose resource r in $P^\prime$ that minimizes Cost(t)
        \If{$AFT(t,r) < Deadline(t)$}
            \State Schedule(t,r)
        \Else
            \State Provision a new resource r
            \State Schedule(t,r)
        \EndIf
    \EndFor
    \State \textbf{return} $P^\prime$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{Deadline distribution algorithm}
\label{alg:deadlinedistribution}
\begin{algorithmic}[1]
\Require w: DAG, d: global deadline
\Ensure Assign sub-deadlines to each task in w
\Procedure{DeadlineDistribution}{$w,d$}
    \State assign $Level(t)$ to each task t in w
    \For{$level\ l\ in\ w$}
        \State $Tasks(l) \gets$ number of tasks in l
        \State $Runtime(l) \gets$ runtime of tasks in l
    \EndFor
    \State $T \gets$ total number of tasks in w
    \State $R \gets$ total runtime of tasks in w
    \State $CP \gets$ critical path of w
    \For{$level\ l\ in\ w$}
        \State $r \gets \alpha * (Runtime(l)/R)$
        \State $t \gets (1-\alpha) * (Tasks(l)/T)$
        \State $FT(l) \gets (r + t) * (d - CP)$
    \EndFor
    \For{$task\ t\ in\ w$}
        \State $est \gets 0$
        \For{p in Pred(t)}
            \State $est \gets Deadline(p)$
        \EndFor
        \State $Deadline(t) \gets est + RT(t) + FT(Level(t))$
    \EndFor
\EndProcedure
\end{algorithmic} 
\end{algorithm}

>>>>

\section{Algorithms}

\subsection{Static Provisioning Dynamic Scheduling (SPDS)}

This is the simplest strategy based on static provisioning of resources and
on-line scheduling of workflow tasks. Given the budget $B$ and deadline $d$
together with the hourly price $p$ of a VM it is possible to compute the number
of VMs $N_{VM}$ to provision so that they consume the whole budget between the
deadline.

\begin{equation}
\label{eq:static-plan}
N_{VM} = \lceil B / d / p \rceil
\end{equation}

Although simple, such provisioning plan has the advantage that it
minimizes the number of provisioning and deprovisioning requests.
Once the resources are provisioned, the tasks are scheduled to VMs using dynamic
priority-based algorithm shown in Algorithm~\ref{alg:ds}.

@@

Initially all the
released tasks from all the workflows are submitted to the queue $Q$. Then, they
are inserted into priority queue $P$ based on the priority of workflows. If
there are free VMs available, the tasks from the priority queue are submitted to
the randomly choosen VMs. The process is repeated each time a task finishes.
Using the priority queue guarantees that tasks from lower priority workflows are
always submitted later than the higher priority ones and that the lower priority
tasks can occupy idle VMs. However, as there is no preemption, long-running
low-priority tasks may delay execution of high-priority tasks when such ones
become ready. Fig.~\ref{fig:spss-example} shows the example plan generated using
SPSS algorithm.

\begin{figure}[htb] 
\centering
\includegraphics[width=1.0\columnwidth]{figures/spds-gantt}
 \caption{Example of schedule generated using SPSS algorithm: tasks are labelled
 by colors depending on the workflow. }
\label{fig:spss-example}
\end{figure}

\subsection{Dynamic Provisioning Dynamic Scheduling (DPDS)}

@@

\begin{algorithm}
\caption{Ensemble planning algorithm}
\label{alg:admit}
\begin{algorithmic}[1]
\Require $W$: workflow ensemble; $b$: budget; $d$: deadline
\Ensure Schedule as much of $W$ as possible given $b$ and $d$
\Procedure{PlanEnsemble}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{DAG planning algorithm}
\label{alg:plandag}
\begin{algorithmic}[1]
\Require $w$: DAG; $P$: current plan; $d$: deadline
\Ensure Create plan for $w$ that minimizes cost and meets deadline $d$
\Procedure{PlanDAG}{$w,P,d$}
    \State $P^\prime\gets$ copy of $P$
    \State \Call{DeadlineDistribution}{w,d}
    \For{$t\ in\ w\ sorted\ by\ Deadline(t)$}
        \State Choose resource r in $P^\prime$ that minimizes Cost(t)
        \If{$AFT(t,r) < Deadline(t)$}
            \State Schedule(t,r)
        \Else
            \State Provision a new resource r
            \State Schedule(t,r)
        \EndIf
    \EndFor
    \State \textbf{return} $P^\prime$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{Deadline distribution algorithm}
\label{alg:deadlinedistribution}
\begin{algorithmic}[1]
\Require $w$: DAG; $d$: global deadline
\Ensure Assign sub-deadlines to each task in w
\Procedure{DeadlineDistribution}{$w,d$}
    \State $T \gets$ total number of tasks in $w$
    \State $R \gets$ total runtime of tasks in $w$
    \State $CP \gets$ length of critical path of $w$
    \State assign $Level(t)$ to each task $t$ in $w$
    \For{level $l\ \in w$}
        \State $Tasks(l) \gets$ number of tasks in $l$
        \State $Runtime(l) \gets$ runtime of tasks in $l$
        \State $r \gets \alpha * (Runtime(l)/R)$
        \State $t \gets (1-\alpha) * (Tasks(l)/T)$
        \State $FT(l) \gets (r + t) * (d - CP)$
    \EndFor
    \For{task $t \in w$}
        \State $LST(t) \gets \max(Deadline(p))\ for\ p \in Pred(t)$
        \State $Deadline(t) \gets LST(t) + RT(t) + FT(Level(t))$
    \EndFor
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{equation}
\label{eq:scaling}
FT(l) = \left[{\alpha}*\frac{T_l}{t}\right] + \left[{(1 - \alpha)}*\frac{R_l}{r} \right]
\end{equation}
